Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-05-14 Chapter-5/5-Preparatory.tex
s

We derive an estimate of the energy loss between the beamline momentum measurement and the TPC ($E_{loss}$) from the Data Driven Monte Carlo using the pion and kaon samples separately, since this quantity is not  measurable directly on data. 
The $E_{loss}$ distribution for the 60A  and 100A pion sample is shown in figure \ref{fig:ELoss60A}, left and right respectively. A clear double peaked structure is visible, which is due to the particles either missing or hitting the HALO paddle: a schematic rendering of this occurrence is  shown in figure \ref{fig:Halo}. The kinematic at WC4 determines the trajectory of a particle and whether or not it will hit the halo paddle. In figure \ref{fig:PxVsXTrue} , we plot the true  $X$ component of the momentum versus the true $X$ position at WC4 for pions missing the halo paddle (left) and for pions hitting the halo paddle (right) for the 60A MC simulation runs -- analogous plots are obtained with the 100A simulation. These distributions can be separated drawing a line in this position-momentum space. 
We use a logistic regression  \cite{agresti2013categorical}  as a classifier to find the best separating line, shown in both plots as the red line. We classify as ``hitting the halo paddle" all pions whose $P_x$ and $X$ are such that $$P_x +0.02* X - 0.4 < 0 $$ and as ``missing the halo  paddle" all pions whose $P_x$ and $X$ are such that $$P_x +0.02*X - 0.4 > 0, $$ where the coefficients of the line are empirically found by the logistic regression estimation. Overall, this simple classifier classifies in the right category (hit or miss) about 86\% of the pion events.
We apply the same classifier on data. We assign  $E_{loss} = 32 \pm 4 $~MeV for events classified as ``hitting the halo paddle"; we assign  $E_{loss} = 24 \pm 3 $~MeV for events classified as ``missing the halo paddle".

@@

\begin{figure}[hbpt]
\centering
\includegraphics[width=0.45\textwidth]{Chapter-5/Images/E_loss60A.png}
\includegraphics[width=0.45\textwidth]{Chapter-5/Images/E_loss100A.png}
\caption{True energy loss between WC4 and the TPC front face according to the MC simulation of the 60A runs (left) and of the 100A runs (right). The distribution for the whole data sample is shown in blue, the distribution for the pions missing the halo is shown in red, and the distribution for the pions hitting the halo is shown in green.  }
\label{fig:ELoss60A}
\end{figure}

>>>>

We derive an estimate of the energy loss between the beamline momentum measurement and the TPC ($E_{loss}$) from the pion DDMC sample, since this quantity is not  measurable directly on data. 
The $E_{loss}$ distribution for the 60A  and 100A pion sample is shown in figure \ref{fig:ELoss60A}, left and right respectively. A clear double peaked structure is visible, which is due to the particles either missing or hitting the HALO paddle: a schematic rendering of this occurrence is  shown in figure \ref{fig:Halo}. The kinematic at WC4 determines the trajectory of a particle and whether or not it will hit the halo paddle. In figure \ref{fig:PxVsXTrue} , we plot the true  horizontal component of the momentum $P_x$ versus the true $X$ position at WC4 for pions missing the halo paddle (left) and for pions hitting the halo paddle (right) for the 60A MC simulation runs -- analogous plots are obtained with the 100A simulation. These distributions can be separated drawing a line in this position-momentum space. 
We use a logistic regression  \cite{agresti2013categorical}  as a classifier to find the best separating line, shown in both plots as the red line. We classify as ``hitting the halo paddle" all pions whose $P_x$ and $X$ are such that $$P_x +0.02* X - 0.4 < 0 $$ and as ``missing the halo  paddle" all pions whose $P_x$ and $X$ are such that $$P_x +0.02*X - 0.4 > 0, $$ where the coefficients of the line are empirically found by the logistic regression estimation. Overall, this simple methode classifies in the right category (hit or miss) about 86\% of the pion events.
We apply the same classifier on data. We assign  $E_{loss} = 32 \pm 4 $~MeV for pion events classified as ``hitting the halo paddle"; we assign  $E_{loss} = 24 \pm 3 $~MeV for pion events classified as ``missing the halo paddle".

@@

\begin{figure}[hbpt]
\centering
\includegraphics[width=0.45\textwidth]{Chapter-5/Images/E_loss60A.png}
\includegraphics[width=0.45\textwidth]{Chapter-5/Images/E_loss100A.png}
\caption{True energy loss between WC4 and the TPC front face according to the MC simulation of negative pions of the 60A runs (left) and of the 100A runs (right). The distribution for the whole data sample is shown in blue, the distribution for the pions missing the halo is shown in red, and the distribution for the pions hitting the halo is shown in green.  }
\label{fig:ELoss60A}
\end{figure}
